---
title: "Empiracle Assignment"
author: "Dave Anderson"
date: "March 8, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gridExtra)
```

#1)
```{r}
a <- c(0.42, 0.06, 0.88, 0.40, 0.90,
0.38, 0.78, 0.71, 0.57, 0.66,
0.48, 0.35, 0.16, 0.22, 0.08,
0.11, 0.29, 0.79, 0.75, 0.82,
0.30, 0.23, 0.01, 0.41, 0.09)


ks.test(a,"punif",0,1)
```
#2)
```{r}
b <- c(25.088, 26.615, 25.468, 27.453, 23.845,
25.996, 26.516, 28.240, 25.980, 30.432,
26.560, 25.844, 26.964, 23.382, 25.282,
24.432, 23.593, 24.644, 26.849, 26.801,
26.303, 23.016, 27.378, 25.351, 23.601,
24.317, 29.778, 29.585, 22.147, 28.352,
29.263, 27.924, 21.579, 25.320, 28.129,
28.478, 23.896, 26.020, 23.750, 24.904,
24.078, 27.228, 27.433, 23.341, 28.923,
24.466, 25.153, 25.893, 26.796, 24.743)

hist(b)
qqnorm(b)


```

```{r}
c <- rnorm(10000,26,2)


hist(c)
ks.test(b,pnorm,26,2)
ks.test(b,c)
```
*The data is normally distributed with a mean of 26 and variance of 4. The histogram looks normal, qqplot looks good. I ran a KS test on both the normal distribution, and a simulated dataset. Interestingly, I accidently included the mean as 28 the first time, and my tests had extremely low p-values. Shows how accurate it is!*

#3)
```{r}
d <- c(0.61, 0.29, 0.06, 0.59,-1.73,
-0.74, 0.51,-0.56,0.39, 1.64,
0.05,-0.06, 0.64,-0.82, 0.31,
1.77, 1.09, -1.28, 2.36, 1.31,
1.05,-0.32,0.40, 1.06,-2.47)

e <- c(2.20, 1.66, 1.38, 0.20,
0.36, 0.00, 0.96, 1.56,
0.44, 1.50,-0.30, 0.66,
2.31, 3.29, -0.27,-0.37,
0.38, 0.70, 0.52,-0.71)

ks.test(d,e)

ks.test(d+2,e)
```
*It seems like X and Y have the same distribution, and X+2 does not have the same distirbution as Y.*

#4)
```{r}
f <- readRDS("norm_sample.Rdata")
g <- rnorm(1000,0,1)
hist(f)
qqnorm(f)
```

```{r}
ks.test(f,"pnorm",0,1)
ks.test(f,g)
```
*Yes, this data does follow the standard normal distribution, but not extremely well.*

```{r}
cdf<- ecdf(f)
```


#5)
```{r}
fiji <- read.table("fijiquakes(1).dat",header = TRUE)
faith <- read.table("faithful(1).dat",header = TRUE)

ecdf_fiji <- ecdf(fiji$mag)
ecdf_faith <- ecdf(faith$waiting)

e_faith <- sqrt(log(2/.1)/(2*272))
e_fiji <- sqrt(log(2/.05)/(2*1000))


answ <- ecdf_fiji(4.9)-ecdf_fiji(4.3)
answ + e_fiji
answ - e_fiji
```
*F(4.9) - F(4.3) 95% confidence interval: [0.48, 0.57]

```{r}
avg <- mean(faith$waiting)

answ2 <- ecdf_faith(mean(avg))

answ2 + e_faith
answ2 - e_faith
```
*The confidence band for the mean waitig time, F(70.9) is[0.32,0.46].*

```{r}
plot(ecdf_faith)
quantile(ecdf_faith,probs = .5)
```
*The median wait time based on our ecdf is 76.*
